\subsection{~Introduction}\label{introduction}

Nuclear magnetic resonance refers to the interaction of a system of
nuclear spins exposed to a static magnetic field with an oscillatory
field, usually in the radio frequency range (anywhere from 1 kHz to
several GHz) cite\{Abraham\}. In the overwhelming majority of cases, the
changes in the spin state that result from this interaction are read out
through a voltage induced by the spin precession into a surrounding
conductor. Even though alternative readout approaches have been
demonstrated, and have their advantages in certain cases, this type of
inductive detection has proven to be both robust and easy to implement.
Indeed, while the earliest demonstrations of nuclear magnetic resonance,
pioneered by Rabi cite\{Rabi:1938tq\}, relied on the deflection atomic
beams in inhomogeneous fields according to the spin state, NMR did not
take off as a widely used tool until the invention of the direct
induction method, independently discovered by Bloch and by Purcell in
1946. Among other advantages, it allows the use of the same structure
for both excitation and detection of the nuclear spin precession.
Particularly in the context of the Fourier spectroscopy method, this has
become very useful. It is relatively easy to expose a sample to an
oscillatory magnetic field by enclosing it in a suitable conductor,
through which an alternating current is sent at the appropriate
frequency. The precessing spins induce a measurable voltage in the same
conductor. Of course, there are technical problems to be solved that
arise due to the high power that is needed in some cases for excitation,
while the induced voltages are very small and require exquisitely
sensitive receivers. It is not uncommon for excitation RF power to
approach several kW, whereas the power available for spin detection is
typically of the order of only a few pW. The earliest inductive NMR
systems have almost exclusively relied on solenoid coils as
excitation/detection systems. As the applications of NMR have
diversified, and new technologies have become available, other
geometries have been explored. In particular, the advent of
superconducting magnets with cylindrical bores has led to the
development of saddle coils and related resonator geometries. Magnetic
resonance imaging, in particular for medical applications, brought the
need to accommodate much larger samples, which was met by the
development of birdcage resonators. Hence, most of the current NMR
detectors follow a roughly cylindrical form factor. There are some
applications, though, which require a more planar geometry. In
particular, the study of thin films, membranes, and interfaces is
complicated in cylindrical detector systems. Special, flattened solenoid
probes have been developed for the study of membrane proteins under
solid-state NMR conditions cite\{Opella\}. As the magnetic fields, and,
correspondingly, the Larmor frequencies used in MRI scanners have
increased, uniform penetration of the radio frequency magnetic fields
into the tissue has become a more and more difficult. Since biological
systems contain ionic solutions, non-conservative electric fields
arising in the detector system need to be shielded from getting in
contact with the tissue. The dielectric losses incurred from interaction
between these electric fields and the tissue degrade the sensitivity of
the detection, but they also lead to excessive power deposition in the
tissue during excitation. As a solution, surface coils for localised MR
imaging of human subjects based on circular or quadratically laid out
strip lines have been proposed. cite\{Zhang:2001js\} NMR spectroscopy is
an extremely versatile tool. Nuclear spins turn out to be excellent
spies. They are well insulated from the noisy electronic degrees of
freedom to allow for long spin coherence life times, which is the basis
of sharp spectral lines. At the same time, the nuclear Larmor frequency
turns out to depend in subtle ways on the electronic environment. In
combination, these two features make it possible to both accurately
measure the nuclear Larmor frequency, and to interpret it in terms of
the molecular environment that surrounds the nucleus. Compared to other
spectroscopic techniques, NMR suffers from a major drawback: its
relative insensitivity. While UV/VIS techniques, in particular
fluorescence, can detect signals from single molecules with relative
ease, NMR typically requires of the order of 10\^{}15 spins to resonate
within a narrow bandwidth (1 Hz or so) in order for the signal to be
measurable. To some extent, this can be alleviated by long measurement
times. Since the signal/noise ratio only grows with the square root of
the measurement time, sensitivity still limits the application of NMR in
practice. The design of NMR detectors that offer optimal sensitivity has
therefore been a long-standing research topic in magnetic resonance.
Sensitivity is determined by the signal/noise ratio that can be obtained
within a specified amount of time from a defined number of spins.
Inductive detectors based on resistive metals invariably produce thermal
noise. Under optimal conditions, where all non-intrinsic sources of
noise have been eliminated by shielding, the blackbody radiation of the
resonator structure itself leads to a noise voltage spectral density
which is essentially independent of frequency, and scales proportionally
to the square root of the ohmic resistance of the detector. The
relationship between the NMR spin precession and the induced voltage
signal has been discussed by Hoult and Richards in terms of the
correspondence principle. The induced signal strength from a single spin
depends on the normalised magnetic field (generated by the detector per
unit current) at the location of the spin. Hence, efficient detectors
need to be designed such that the magnetic field they generate per unit
current is maximal. This conflicts with the requirement of low
resistance, which is important to keep the noise voltage small, and an
optimal compromise must be found in practice between the two. It has
been well known for about two decades that the mass sensitivity (i.e.,
the signal/noise ratio per spin) of inductive detectors is roughly
inversely proportional to the detector size. This can be rationalised by
examining the normalised magnetic field and the radio frequency
resistance of a particular detector geometry as a function of its
overall dimensions. For example, the magnetic field generated by a
single circular loop of diameter d made of a wire of thickness h is
given approximately by \(H/I=1/(pi d)\). If the geometry is scaled by a
factor \(alpha\), the \(H/I\) value therefore scales as \(alpha^{-1}\).
At typical NMR frequencies, the skin depth in Cu amounts only to a few
\(mu\)m. Therefore, as the both the wire diameter and the loop diameter
are scaled by the same factor \(alpha\), the resistance of the structure
remains roughly constant, as long as the wire diameter remains larger
than the skin depth. As a result the signal to noise ratio is expected
to scale roughly as \(1/alpha\). A similar argument can be made for
solenoid coils. In practice, the observed scaling is weaker. Still, NMR
detectors based on micro coils (i.e., with dimensions of tens to
hundreds of \(mu\)m) have been shown to provide very high mass
sensitivities. This has formed the basis of hyphenated techniques, where
upstream chromatographic separation is combined with downstream
detection by an NMR system equipped with a micro
detector.cite\{webb2005nmr\} Microfluidics is a rapidly expanding field
of science and technology. The underlying idea is borrowed from micro
electronics: to integrate complex functionality in a mostly
two-dimensional layout, making use of efficient lithographic fabrication
technologies. This lab-on-a-chip (LoC) approach has proven especially
fruitful in enabling total analysis systems, which integrate sample
preparation, chromatographic separation, and detection on single chip
platform. cite\{Manz:1990tj\} Since lithographic techniques allow the
accurate reproduction of complex and very highly resolved features,
microfluidic systems can be designed to mimic highly complex
environments with great control and accuracy. This enables the culture
of biological systems under artificial and highly controlled conditions,
while closely mimicking the natural environment. This has become an
invaluable tool for the study of differentiated cells, their
development, and the interplay between different cell types.
\{\textbf{REFS needed!!}\} NMR spectroscopy is uniquely suited to
observe metabolic processes in live systems. It therefore has great
potential as an observation tool in microfluidic culture assays.
However, in spite of significant efforts, its use in the context of
microfluidic devices is not yet widespread. There are a number of
reasons for this. On the one hand, the planar geometry of microfluidic
devices is not easily combined with common NMR detectors, which are
typically designed for a cylindrical sample. Another limitation is the
poor sensitivity of NMR, which is exacerbated by the small sample
amounts typically available in microfluidic systems. As will become
apparent in the following, micro stripline detectors are of particular
interest in this context, since they inherently follow a planar
geometry, and they can offer extremely high mass sensitivity. The first
NMR probes based on a strip line geometry have been proposed in the
context of magnetic resonance imaging. Their use for NMR spectroscopy at
the microscope was first proposed by Maguire et al
cite\{maguire2004sas\} in 2004. They integrated a stripline containing a
small slot into a radio frequency resonator. The slot leads to current
crowding, and consequently to a very large \(H/I\) value locally. This
geometry provides excellent mass sensitivity, but the achieved spectral
resolution was still relatively poor. A few years later, van Bentum and
Kentgens and coworkers proposed a stripline detector based on a
symmetric geometry with ground planes on either side of the strip line.
By tapering the transition in the width of the strip line broadening of
the resonance lines due to magnetic susceptibility artefacts could be
largely reduced, cite\{Bart:2009er\} leading to excellent performance in
terms of resolution. While these probes were operated in a flow mode,
with fixed capillaries acting as sample holders, this geometry has
recently been modified by Finch et al. to a transmission line probe
based on two identical planar conductors, which can accommodate an
exchangeable microfluidic chip. Looking into the future, strip line
based detector geometries offer significant potential for further
advances in miniaturisation. Their fabrication using lithographic
techniques is straightforward, in contrast to intrinsically
three-dimensional geometries such as solenoids, and there is no reason
why they could not be successfully applied to detectors an order of
magnitude or more smaller than the ones that have been demonstrated so
far. Another exciting possibility is the use of stripline detectors in
travelling wave mode, rather than as resonators carrying standing waves.
Travelling wave NMR, which been demonstrated in the context of magnetic
resonance imaging and (macroscopic) NMR spectroscopy, could have
signifiant advantages at the micro scale, since it allows the spatial
separation of the sample and the detection circuitry. The remainder of
this chapter is organised as follows: first, some theoretical aspects of
strip lines and strip-line based resonators are examined in section 2.
Section 3 provides a chronological overview of the development of
micro-NMR strip line and micro strip based detectors, and finally,
section 4 discusses some of the recently demonstrated applications.
