%!TEX root = microstrip.tex

% Review on Micro-Striplines and Micro-Slot probes
% Marcel Utz and Ali Yilmaz
% February 2016

\section{Introduction}

In nuclear magnetic resonance, a system of nuclear spins exposed to a static 
magnetic interacts with an oscillatory field, usually in the radio frequency range 
\cite{Abragam:1961vg}. 
In most NMR setups, including all in all commercially available NMR
spectrometers, coherent transitions between spin
states are detected by a voltage induced into a 
conductor surrounding the sample. 
While other have 
their advantages in certain cases, inductive detection has proven to be both robust and 
easy to implement. 

The earliest demonstrations of nuclear magnetic resonance, pioneered 
by Rabi \cite{Rabi:1938tq}, have relied on the deflection atomic beams in inhomogeneous fields according to the spin state, rather than on inductive detection.
However, NMR only became a widely used tool for chemistry after the invention of the direct induction 
method, independently discovered by Bloch \cite{Bloch:1946hk} 
and by Purcell, Torrey, and Pound \cite{Purcell:1946ft} in 1946. 

The same conductor that detects the nuclear spin precession can also be used for its excitation. 
Particularly in the context of the Fourier spectroscopy method \cite{Ernst:1966cr}, this has 
become very useful. It is relatively easy to expose a sample to an oscillatory magnetic field by 
surrounding it with a suitable conductor, through which an alternating current is sent at the appropriate 
frequency. The precessing spins induce a measurable voltage in the same conductor. There are 
technical problems to be solved that arise due to the high power that is needed in some cases for 
excitation, while the induced voltages are very small and require exquisitely sensitive receivers. It 
is not uncommon for excitation RF power to approach several kW, whereas the power available for spin 
detection is many orders of magnitude lower.

The earliest inductive NMR systems have almost exclusively relied on solenoid coils as excitation/
detection systems. As the applications of NMR have diversified, and new technologies have become 
available, other geometries have been explored. In the 1970s, electromagnets
with planar gaps were replaced by superconducting solenoids, which offered
higher fields and better stability. To facilitate loading samples 
axially through be magnet bore, saddle coils and related resonator geometries have been developed.  At the same time, magnetic resonance imaging, in particular for medical applications, brought the need to accommodate  much larger samples. 

Today, most detectors used in NMR spectroscopy follow a cylindrical form factor, optimised for standard NMR sample tubes of 5~mm or 10~mm diameter.
Some special
applications, though, require a different geometry, and  In particular, the study of thin films, 
membranes, and interfaces is inefficient in cylindrical detectors, and various
alternative detector geometries have been explored. For example, 
flattened solenoid 
probes have been developed for the study of membrane proteins under solid-state NMR conditions
\cite{Bechinger:1991in}. 

The present chapter is concerned with the use of planar waveguides, such as striplines
and microstrips, as inductive detectors for NMR spectroscopy and imaging. As 
will become clear in the following, such structures readily lend themselves
to miniaturisation, since they can be fabricated using efficient lithographic
techniques. However, they were introduced as detectors in magnetic 
resonance imaging long before their potential for micro-NMR was discovered.

As the magnetic fields, and, correspondingly, the Larmor frequencies used in MRI scanners 
have increased, uniform penetration of the radio frequency magnetic fields into the tissue has become 
more and more difficult. Since biological systems contain ionic solutions, non-conservative electric 
fields arising in the detector system need to be shielded from getting in contact with the tissue. The 
dielectric losses incurred from interaction between these electric fields and the tissue degrade the 
sensitivity of the detection, but they also lead to excessive power deposition in the tissue during 
excitation. As a solution, surface coils for localised MR imaging of human subjects based on circular 
or quadratically laid out strip lines have been proposed \cite{Zhang:2001js}.


Compared to many other spectroscopic techniques, NMR suffers from a major drawback: its relative 
insensitivity. While UV/VIS techniques, in particular fluorescence, can detect signals from single 
molecules with relative ease, NMR typically requires of the order of $10^{15}$ spins to resonate within a 
narrow bandwidth (1 Hz or so) in order for the signal to be measurable. 
The design of NMR detectors that offer optimal sensitivity has therefore been a long-standing research 
topic. Sensitivity is determined by the signal/noise ratio that can be obtained 
within a specified amount of time from a defined number of spins. Inductive detectors based on 
resistive metals invariably produce thermal noise. Under optimal conditions, where all non-intrinsic 
sources of noise have been eliminated by shielding, the blackbody radiation of the resonator structure 
itself leads to a noise voltage spectral density which is essentially independent of frequency, and 
scales proportionally to the square root of the ohmic resistance of the detector. 

The relationship 
between the NMR spin precession and the induced voltage signal has been discussed by Hoult and Richards 
in terms of the correspondence principle \cite{hoult1975cfd}. The  induced signal strength from a single spin depends on 
the normalised magnetic field at the location of the spin that the detector circuit produces per 
unit current flowing in it. 
Hence, efficient detectors need to be designed such that the magnetic field they generate is maximal. This conflicts with the requirement of low ohmic resistance, which is important to keep 
the noise voltage small, and a compromise between the two must be found in practice.

It has been well known for about two decades that the mass sensitivity (i.e., the signal/noise ratio 
per spin and per bandwidth) of inductive detectors is roughly inversely proportional to the detector size. This can be 
rationalised by examining the normalised magnetic field and the radio frequency resistance of a 
particular detector geometry as a function of its overall dimensions. For example, the magnetic field 
generated at the centre of a circular loop of diameter $d$ made of a wire of thickness $h$ is given approximately 
by $H/I=1/(\pi d)$. If the geometry is scaled by a factor $\alpha$, $H/I$ therefore scales as 
$\alpha^{-1}$. At typical NMR frequencies, the skin depth in Cu amounts only to a few $\mu$m. Therefore, 
as both the wire diameter and the loop diameter are scaled by the same factor $\alpha$, the 
resistance of the structure remains roughly constant, as long as the wire diameter remains larger than 
the skin depth. As a result the signal to noise ratio for a given number of spins is expected to scale roughly as $1/\alpha$. A 
similar argument can be made for solenoid coils and other detector geometries.

Microfluidics represents a rapidly expanding field of science and technology. The underlying idea is borrowed 
from micro-electronics: to integrate complex functionality in a mostly two-dimensional layout, making 
use of efficient lithographic fabrication technologies. This lab-on-a-chip (LoC) approach has proven 
especially fruitful in enabling total analysis systems, which integrate sample preparation, 
chromatographic separation, and detection on single chip platform \cite{Manz:1990vc}.

Since lithographic techniques allow the accurate reproduction of complex and very highly resolved 
features, microfluidic systems can be designed to mimic highly complex environments with great control 
and accuracy. This enables the culture of biological systems under artificial and highly controlled 
conditions, while closely mimicking the natural environment. This has become an invaluable tool for the 
study of  differentiated cells, their development, and the interplay between different cell types. 

NMR spectroscopy is uniquely suited to observe metabolic processes in live systems. It therefore has 
great potential as an observation tool in microfluidic culture assays. However, in spite of significant 
efforts, its use in the context of microfluidic devices is not yet widespread. There are a number of 
reasons for this. On the one hand, the planar geometry of microfluidic devices is not easily combined 
with common NMR detectors, which are typically designed for a cylindrical sample. Another limitation is 
the poor sensitivity of NMR, which is exacerbated by the small sample amounts typically available in 
microfluidic systems. Stripline and microstrip detectors are of 
particular interest in this context, since they inherently follow a planar geometry, and they can offer 
extremely high mass sensitivity, as will be discussed in detail in the following.

Looking into the future, transmission-line based detector geometries offer significant potential for further 
advances in miniaturisation. Their fabrication using lithographic techniques is straightforward, in 
contrast to intrinsically three-dimensional geometries such as solenoids, and there is no reason why 
they could not be successfully applied to detectors an order of magnitude or more smaller than the ones 
that have been demonstrated so far. Another exciting possibility is the use of transmission line detectors in 
travelling wave mode, rather than as resonators carrying standing waves. Travelling wave NMR, which 
has been demonstrated in the context of magnetic resonance imaging and (macroscopic) NMR spectroscopy, 
could have signifiant advantages at the micro scale, since it allows the spatial separation of the 
sample and the detection circuitry. 
